---
title: "Getting Started with roller"
author: "Jeonghyeon Dang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(roller)
```

##Rolling a object

The package `"roller"` is a minimal implementation for simulating rolling a object a given number of times, and to visualize the relative frequencies in such a series of rolling.

The first step is to create a `"fair_coin"`

##Creating a object
```{r}
fair_coin <- device()
fair_coin
```

By default, `device()` creates a _fair_ coin with standard sides `1`, and `2`, and with probability values for each side of 0.5


##Checking class
```{r}
is.device(fair_coin)
```

We can check the class of fair_coin. If it is class of device, then output comes with TRUE, if not FALSE

```{r}
fair_die <- device(sides = 1:6, prob = rep(1/6, 6))
```

We also can make 6 sides of fair dice

##Object "rolls"
```{r}
fair_die <- device() 
set.seed(123)
fair50 <- roll(fair_die, times = 50) 
fair50
```

